---
title: 'R-Workshop: Effects of Illegitimate Work Tasks on Strain Anticipation'
date: "`r Sys.Date()`"
output: 
  html_document
toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library("install.load")

install_load("installr",
             "tidyverse",
             "summarytools",
             "skimr",
             "psych",
             "interactions")
```

# Import Data

```{r}
ws <- read.csv("ws_data.csv")
```

# Data Preparation 

## Reverse Items 

```{r}
ws <- ws %>% 
  mutate(DA_ANTC_02_t1 = 101 - DA_ANTC_02_r_t1,
         DA_ANTC_02_t2 = 101 - DA_ANTC_02_r_t2,
         DA_ANTC_02_t3 = 101 - DA_ANTC_02_r_t3,
         DA_ANTC_02_t4 = 101 - DA_ANTC_02_r_t4,
         DA_ANTC_02_t5 = 101 - DA_ANTC_02_r_t5,
         DA_ANTC_02_t6 = 101 - DA_ANTC_02_r_t6,
         DA_ANTC_02_t7 = 101 - DA_ANTC_02_r_t7,
         DA_ANTC_02_t8 = 101 - DA_ANTC_02_r_t8,
         DA_ANTC_02_t9 = 101 - DA_ANTC_02_r_t9,
         DA_ANTC_02_t10 = 101 - DA_ANTC_02_r_t10)
```

## Include NA option 

```{r}
ws <- ws %>%
  mutate(across(starts_with("DA_PSYSAFE_"), ~ na_if(., 6)))
```

# Aggregate Data 

## Illegitimate Work Tasks 

### Within occasions 

T1

```{r}
ws <- ws %>%
  mutate(ILWOTA_t1 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t1,
             DA_ILWOTA_02_t1,
             DA_ILWOTA_03_t1,
             DA_ILWOTA_04_t1)),
           na.rm = TRUE))
```

T2

```{r}
ws <- ws %>%
  mutate(ILWOTA_t2 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t2,
             DA_ILWOTA_02_t2,
             DA_ILWOTA_03_t2,
             DA_ILWOTA_04_t2)),
           na.rm = TRUE))
```

T3

```{r}
ws <- ws %>%
  mutate(ILWOTA_t3 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t3,
             DA_ILWOTA_02_t3,
             DA_ILWOTA_03_t3,
             DA_ILWOTA_04_t3)),
           na.rm = TRUE))
```

T4

```{r}
ws <- ws %>%
  mutate(ILWOTA_t4 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t4,
             DA_ILWOTA_02_t4,
             DA_ILWOTA_03_t4,
             DA_ILWOTA_04_t4)),
           na.rm = TRUE))
```

T5

```{r}
ws <- ws %>%
  mutate(ILWOTA_t5 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t5,
             DA_ILWOTA_02_t5,
             DA_ILWOTA_03_t5,
             DA_ILWOTA_04_t5)),
           na.rm = TRUE))
```

T6

```{r}
ws <- ws %>%
  mutate(ILWOTA_t6 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t6,
             DA_ILWOTA_02_t6,
             DA_ILWOTA_03_t6,
             DA_ILWOTA_04_t6)),
           na.rm = TRUE))
```

T7

```{r}
ws <- ws %>%
  mutate(ILWOTA_t7 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t7,
             DA_ILWOTA_02_t7,
             DA_ILWOTA_03_t7,
             DA_ILWOTA_04_t7)),
           na.rm = TRUE))
```

T8

```{r}
ws <- ws %>%
  mutate(ILWOTA_t8 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t8,
             DA_ILWOTA_02_t8,
             DA_ILWOTA_03_t8,
             DA_ILWOTA_04_t8)),
           na.rm = TRUE))
```

T9

```{r}
ws <- ws %>%
  mutate(ILWOTA_t9 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t9,
             DA_ILWOTA_02_t9,
             DA_ILWOTA_03_t9,
             DA_ILWOTA_04_t9)),
           na.rm = TRUE))
```

T10

```{r}
ws <- ws %>%
  mutate(ILWOTA_t10 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t10,
             DA_ILWOTA_02_t10,
             DA_ILWOTA_03_t10,
             DA_ILWOTA_04_t10)),
           na.rm = TRUE))
```

### Between occasions 

```{r}
ws <- ws %>%
  mutate(ILWOTA = rowMeans(select(ws,
           c(ILWOTA_t1,
             ILWOTA_t2,
             ILWOTA_t3,
             ILWOTA_t4,
             ILWOTA_t5,
             ILWOTA_t6,
             ILWOTA_t7,
             ILWOTA_t8,
             ILWOTA_t9,
             ILWOTA_t10)),
           na.rm = TRUE))
```

## Psychological Safety 

### Within Occasions 

T1

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t1 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t1,
             DA_PSYSAFE_02_t1,
             DA_PSYSAFE_03_t1,
             DA_PSYSAFE_04_t1,
             DA_PSYSAFE_05_t1,
             DA_PSYSAFE_06_t1)),
           na.rm = TRUE))
```

T2

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t2 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t2,
             DA_PSYSAFE_02_t2,
             DA_PSYSAFE_03_t2,
             DA_PSYSAFE_04_t2,
             DA_PSYSAFE_05_t2,
             DA_PSYSAFE_06_t2)),
           na.rm = TRUE))
```

T3

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t3 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t3,
             DA_PSYSAFE_02_t3,
             DA_PSYSAFE_03_t3,
             DA_PSYSAFE_04_t3,
             DA_PSYSAFE_05_t3,
             DA_PSYSAFE_06_t3)),
           na.rm = TRUE))
```

T4

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t4 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t4,
             DA_PSYSAFE_02_t4,
             DA_PSYSAFE_03_t4,
             DA_PSYSAFE_04_t4,
             DA_PSYSAFE_05_t4,
             DA_PSYSAFE_06_t4)),
           na.rm = TRUE))
```

T5

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t5 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t5,
             DA_PSYSAFE_02_t5,
             DA_PSYSAFE_03_t5,
             DA_PSYSAFE_04_t5,
             DA_PSYSAFE_05_t5,
             DA_PSYSAFE_06_t5)),
           na.rm = TRUE))
```

T6

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t6 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t6,
             DA_PSYSAFE_02_t6,
             DA_PSYSAFE_03_t6,
             DA_PSYSAFE_04_t6,
             DA_PSYSAFE_05_t6,
             DA_PSYSAFE_06_t6)),
           na.rm = TRUE))
```

T7

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t7 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t7,
             DA_PSYSAFE_02_t7,
             DA_PSYSAFE_03_t7,
             DA_PSYSAFE_04_t7,
             DA_PSYSAFE_05_t7,
             DA_PSYSAFE_06_t7)),
           na.rm = TRUE))
```

T8

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t8 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t8,
             DA_PSYSAFE_02_t8,
             DA_PSYSAFE_03_t8,
             DA_PSYSAFE_04_t8,
             DA_PSYSAFE_05_t8,
             DA_PSYSAFE_06_t8)),
           na.rm = TRUE))
```

T9

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t9 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t9,
             DA_PSYSAFE_02_t9,
             DA_PSYSAFE_03_t9,
             DA_PSYSAFE_04_t9,
             DA_PSYSAFE_05_t9,
             DA_PSYSAFE_06_t9)),
           na.rm = TRUE))
```

T10

```{r}
ws <- ws %>%
  mutate(PSYSAFE_t10 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t10,
             DA_PSYSAFE_02_t10,
             DA_PSYSAFE_03_t10,
             DA_PSYSAFE_04_t10,
             DA_PSYSAFE_05_t10,
             DA_PSYSAFE_06_t10)),
           na.rm = TRUE))
```

### Between Occasions 

```{r}
ws <- ws %>%
  mutate(PSYSAFE = rowMeans(select(ws,
           c(PSYSAFE_t1,
             PSYSAFE_t2,
             PSYSAFE_t3,
             PSYSAFE_t4,
             PSYSAFE_t5,
             PSYSAFE_t6,
             PSYSAFE_t7,
             PSYSAFE_t8,
             PSYSAFE_t9,
             PSYSAFE_t10)),
           na.rm = TRUE))
```

## Anger 

### Within Occasions 

T1

```{r}
ws <- ws %>%
  mutate(ANG_t1 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t1,
             DA_MOOD_ANG_02_t1,
             DA_MOOD_ANG_03_t1)),
           na.rm = TRUE))
```

T2

```{r}
ws <- ws %>%
  mutate(ANG_t2 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t2,
             DA_MOOD_ANG_02_t2,
             DA_MOOD_ANG_03_t2)),
           na.rm = TRUE))
```

T3

```{r}
ws <- ws %>%
  mutate(ANG_t3 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t3,
             DA_MOOD_ANG_02_t3,
             DA_MOOD_ANG_03_t3)),
           na.rm = TRUE))
```

T4

```{r}
ws <- ws %>%
  mutate(ANG_t4 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t4,
             DA_MOOD_ANG_02_t4,
             DA_MOOD_ANG_03_t4)),
           na.rm = TRUE))
```

T5

```{r}
ws <- ws %>%
  mutate(ANG_t5 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t5,
             DA_MOOD_ANG_02_t5,
             DA_MOOD_ANG_03_t5)),
           na.rm = TRUE))
```

T6

```{r}
ws <- ws %>%
  mutate(ANG_t6 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t6,
             DA_MOOD_ANG_02_t6,
             DA_MOOD_ANG_03_t6)),
           na.rm = TRUE))
```

T7

```{r}
ws <- ws %>%
  mutate(ANG_t7 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t7,
             DA_MOOD_ANG_02_t7,
             DA_MOOD_ANG_03_t7)),
           na.rm = TRUE))
```

T8

```{r}
ws <- ws %>%
  mutate(ANG_t8 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t8,
             DA_MOOD_ANG_02_t8,
             DA_MOOD_ANG_03_t8)),
           na.rm = TRUE))
```

T9

```{r}
ws <- ws %>%
  mutate(ANG_t9 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t9,
             DA_MOOD_ANG_02_t9,
             DA_MOOD_ANG_03_t9)),
           na.rm = TRUE))
```

T10

```{r}
ws <- ws %>%
  mutate(ANG_t10 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t10,
             DA_MOOD_ANG_02_t10,
             DA_MOOD_ANG_03_t10)),
           na.rm = TRUE))
```

### Between Occasions

```{r}
ws <- ws %>%
  mutate(ANG = rowMeans(select(ws,
           c(ANG_t1,
             ANG_t2,
             ANG_t3,
             ANG_t4,
             ANG_t5,
             ANG_t6,
             ANG_t7,
             ANG_t8,
             ANG_t9,
             ANG_t10)),
           na.rm = TRUE))
```

## Strain Anticipation 

### Within Occasions 

T1

```{r}
ws <- ws %>%
  mutate(SA_t1 = rowMeans(select(ws,
           c(DA_ANTC_01_t1,
             DA_ANTC_02_t1)),
           na.rm = TRUE))
```

T2

```{r}
ws <- ws %>%
  mutate(SA_t2 = rowMeans(select(ws,
           c(DA_ANTC_01_t2,
             DA_ANTC_02_t2)),
           na.rm = TRUE))
```

T3

```{r}
ws <- ws %>%
  mutate(SA_t3 = rowMeans(select(ws,
           c(DA_ANTC_01_t3,
             DA_ANTC_02_t3)),
           na.rm = TRUE))
```

T4

```{r}
ws <- ws %>%
  mutate(SA_t4 = rowMeans(select(ws,
           c(DA_ANTC_01_t4,
             DA_ANTC_02_t4)),
           na.rm = TRUE))
```

T5

```{r}
ws <- ws %>%
  mutate(SA_t5 = rowMeans(select(ws,
           c(DA_ANTC_01_t5,
             DA_ANTC_02_t5)),
           na.rm = TRUE))
```

T6

```{r}
ws <- ws %>%
  mutate(SA_t6 = rowMeans(select(ws,
           c(DA_ANTC_01_t6,
             DA_ANTC_02_t6)),
           na.rm = TRUE))
```

T7

```{r}
ws <- ws %>%
  mutate(SA_t7 = rowMeans(select(ws,
           c(DA_ANTC_01_t7,
             DA_ANTC_02_t7)),
           na.rm = TRUE))
```

T8

```{r}
ws <- ws %>%
  mutate(SA_t8 = rowMeans(select(ws,
           c(DA_ANTC_01_t8,
             DA_ANTC_02_t8)),
           na.rm = TRUE))
```

T9

```{r}
ws <- ws %>%
  mutate(SA_t9 = rowMeans(select(ws,
           c(DA_ANTC_01_t9,
             DA_ANTC_02_t9)),
           na.rm = TRUE))
```

T10

```{r}
ws <- ws %>%
  mutate(SA_t10 = rowMeans(select(ws,
           c(DA_ANTC_01_t10,
             DA_ANTC_02_t10)),
           na.rm = TRUE))
```


### Between Occasions 

```{r}
ws <- ws %>%
  mutate(SA = rowMeans(select(ws,
           c(SA_t1,
             SA_t2,
             SA_t3,
             SA_t4,
             SA_t5,
             SA_t6,
             SA_t7,
             SA_t8,
             SA_t9,
             SA_t10)),
           na.rm = TRUE))
```

# Descriptive Statistics 

## Frequencies

```{r}
freq(ws$ST_GENDER)
```

## Means; SD 

### Age 

```{r}
ws %>% skim(ST_AGE)
```

### Study Variables 

#### Illegitimate Work Tasks 

```{r}
ws %>% skim(ILWOTA)
```

#### Psychological Safety 

```{r}
ws %>% skim(PSYSAFE)
```

#### Anger 

```{r}
ws %>% skim(ANG)
```

#### Strain Anticipation 

```{r}
ws %>% skim(SA)
```

## Bivariate Correlation Matrix

```{r}
cor_dat <- ws %>%
  select(ILWOTA,
         PSYSAFE,
         ANG,
         SA)
```


```{r}
corr.test(cor_dat)
```

# Inference Statistics

## Simple regression 

unstandardized coefficients

```{r}
summary(lm(SA~ILWOTA, data = ws))
```

standardize predictor & dependent variable

```{r}
ws <- ws %>% 
  mutate(
    ILWOTA_s = scale(ILWOTA, center = T, scale =T)
    , SA_s = scale(SA, center = T, scale =T)
    )
```

standardized coefficients 

```{r}
summary(lm(SA_s~ILWOTA_s, data = ws))
```


## Moderation 

Center variables

```{r}
ws <- ws %>% 
  mutate(ILWOTA_c = scale(ILWOTA, center = T, scale = F),
         PSYSAFE_c = scale(PSYSAFE, center = T, scale = F))
```

Compute moderation model

```{r}
summary(lm(SA~ILWOTA_c*PSYSAFE_c, data = ws))
```

Visualize moderation effect

```{r}
interact_plot(
  lm(SA ~ ILWOTA_c * PSYSAFE_c, data = ws),
  pred = ILWOTA_c,
  modx = PSYSAFE_c,
  interval = T,
)
```

Johnson-Neyman intervals

```{r}
johnson_neyman(
  lm(SA ~ ILWOTA_c * PSYSAFE_c, data = ws)
  , pred = ILWOTA_c
  , modx = PSYSAFE_c
  , control.fdr=T)
```



## Mediation 

```{r}
set.seed(42)
print(mediate(SA ~ ILWOTA + (ANG), data=ws))
```

# Session Info

```{r}
sessionInfo()
```

