---
title: "R workshop - Addon: Bootstrap"
author: "Bernhard Piskernik"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, results = 'hide', warning = F)
```


```{r}
library("install.load")

install_load("installr",
             "tidyverse",
             "summarytools",
             "skimr",
             "psych",
             "interactions")
```


```{r}
ws <- read.csv("ws_data.csv")
```



```{r}
ws <- ws %>% 
  mutate(DA_ANTC_02_t1 = 101 - DA_ANTC_02_r_t1,
         DA_ANTC_02_t2 = 101 - DA_ANTC_02_r_t2,
         DA_ANTC_02_t3 = 101 - DA_ANTC_02_r_t3,
         DA_ANTC_02_t4 = 101 - DA_ANTC_02_r_t4,
         DA_ANTC_02_t5 = 101 - DA_ANTC_02_r_t5,
         DA_ANTC_02_t6 = 101 - DA_ANTC_02_r_t6,
         DA_ANTC_02_t7 = 101 - DA_ANTC_02_r_t7,
         DA_ANTC_02_t8 = 101 - DA_ANTC_02_r_t8,
         DA_ANTC_02_t9 = 101 - DA_ANTC_02_r_t9,
         DA_ANTC_02_t10 = 101 - DA_ANTC_02_r_t10)
```


```{r}
ws <- ws %>%
  mutate(across(starts_with("DA_PSYSAFE_"), ~ na_if(., 6)))
```



```{r}
ws <- ws %>%
  mutate(ILWOTA_t1 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t1,
             DA_ILWOTA_02_t1,
             DA_ILWOTA_03_t1,
             DA_ILWOTA_04_t1)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ILWOTA_t2 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t2,
             DA_ILWOTA_02_t2,
             DA_ILWOTA_03_t2,
             DA_ILWOTA_04_t2)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ILWOTA_t3 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t3,
             DA_ILWOTA_02_t3,
             DA_ILWOTA_03_t3,
             DA_ILWOTA_04_t3)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ILWOTA_t4 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t4,
             DA_ILWOTA_02_t4,
             DA_ILWOTA_03_t4,
             DA_ILWOTA_04_t4)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ILWOTA_t5 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t5,
             DA_ILWOTA_02_t5,
             DA_ILWOTA_03_t5,
             DA_ILWOTA_04_t5)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ILWOTA_t6 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t6,
             DA_ILWOTA_02_t6,
             DA_ILWOTA_03_t6,
             DA_ILWOTA_04_t6)),
           na.rm = TRUE))
```



```{r}
ws <- ws %>%
  mutate(ILWOTA_t7 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t7,
             DA_ILWOTA_02_t7,
             DA_ILWOTA_03_t7,
             DA_ILWOTA_04_t7)),
           na.rm = TRUE))
```



```{r}
ws <- ws %>%
  mutate(ILWOTA_t8 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t8,
             DA_ILWOTA_02_t8,
             DA_ILWOTA_03_t8,
             DA_ILWOTA_04_t8)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ILWOTA_t9 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t9,
             DA_ILWOTA_02_t9,
             DA_ILWOTA_03_t9,
             DA_ILWOTA_04_t9)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ILWOTA_t10 = rowMeans(select(ws,
           c(DA_ILWOTA_01_t10,
             DA_ILWOTA_02_t10,
             DA_ILWOTA_03_t10,
             DA_ILWOTA_04_t10)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ILWOTA = rowMeans(select(ws,
           c(ILWOTA_t1,
             ILWOTA_t2,
             ILWOTA_t3,
             ILWOTA_t4,
             ILWOTA_t5,
             ILWOTA_t6,
             ILWOTA_t7,
             ILWOTA_t8,
             ILWOTA_t9,
             ILWOTA_t10)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t1 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t1,
             DA_PSYSAFE_02_t1,
             DA_PSYSAFE_03_t1,
             DA_PSYSAFE_04_t1,
             DA_PSYSAFE_05_t1,
             DA_PSYSAFE_06_t1)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t2 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t2,
             DA_PSYSAFE_02_t2,
             DA_PSYSAFE_03_t2,
             DA_PSYSAFE_04_t2,
             DA_PSYSAFE_05_t2,
             DA_PSYSAFE_06_t2)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t3 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t3,
             DA_PSYSAFE_02_t3,
             DA_PSYSAFE_03_t3,
             DA_PSYSAFE_04_t3,
             DA_PSYSAFE_05_t3,
             DA_PSYSAFE_06_t3)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t4 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t4,
             DA_PSYSAFE_02_t4,
             DA_PSYSAFE_03_t4,
             DA_PSYSAFE_04_t4,
             DA_PSYSAFE_05_t4,
             DA_PSYSAFE_06_t4)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t5 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t5,
             DA_PSYSAFE_02_t5,
             DA_PSYSAFE_03_t5,
             DA_PSYSAFE_04_t5,
             DA_PSYSAFE_05_t5,
             DA_PSYSAFE_06_t5)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t6 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t6,
             DA_PSYSAFE_02_t6,
             DA_PSYSAFE_03_t6,
             DA_PSYSAFE_04_t6,
             DA_PSYSAFE_05_t6,
             DA_PSYSAFE_06_t6)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t7 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t7,
             DA_PSYSAFE_02_t7,
             DA_PSYSAFE_03_t7,
             DA_PSYSAFE_04_t7,
             DA_PSYSAFE_05_t7,
             DA_PSYSAFE_06_t7)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t8 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t8,
             DA_PSYSAFE_02_t8,
             DA_PSYSAFE_03_t8,
             DA_PSYSAFE_04_t8,
             DA_PSYSAFE_05_t8,
             DA_PSYSAFE_06_t8)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t9 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t9,
             DA_PSYSAFE_02_t9,
             DA_PSYSAFE_03_t9,
             DA_PSYSAFE_04_t9,
             DA_PSYSAFE_05_t9,
             DA_PSYSAFE_06_t9)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE_t10 = rowMeans(select(ws,
           c(DA_PSYSAFE_01_t10,
             DA_PSYSAFE_02_t10,
             DA_PSYSAFE_03_t10,
             DA_PSYSAFE_04_t10,
             DA_PSYSAFE_05_t10,
             DA_PSYSAFE_06_t10)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(PSYSAFE = rowMeans(select(ws,
           c(PSYSAFE_t1,
             PSYSAFE_t2,
             PSYSAFE_t3,
             PSYSAFE_t4,
             PSYSAFE_t5,
             PSYSAFE_t6,
             PSYSAFE_t7,
             PSYSAFE_t8,
             PSYSAFE_t9,
             PSYSAFE_t10)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ANG_t1 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t1,
             DA_MOOD_ANG_02_t1,
             DA_MOOD_ANG_03_t1)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ANG_t2 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t2,
             DA_MOOD_ANG_02_t2,
             DA_MOOD_ANG_03_t2)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ANG_t3 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t3,
             DA_MOOD_ANG_02_t3,
             DA_MOOD_ANG_03_t3)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ANG_t4 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t4,
             DA_MOOD_ANG_02_t4,
             DA_MOOD_ANG_03_t4)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ANG_t5 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t5,
             DA_MOOD_ANG_02_t5,
             DA_MOOD_ANG_03_t5)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ANG_t6 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t6,
             DA_MOOD_ANG_02_t6,
             DA_MOOD_ANG_03_t6)),
           na.rm = TRUE))
```

```{r}
ws <- ws %>%
  mutate(ANG_t7 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t7,
             DA_MOOD_ANG_02_t7,
             DA_MOOD_ANG_03_t7)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ANG_t8 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t8,
             DA_MOOD_ANG_02_t8,
             DA_MOOD_ANG_03_t8)),
           na.rm = TRUE))
```



```{r}
ws <- ws %>%
  mutate(ANG_t9 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t9,
             DA_MOOD_ANG_02_t9,
             DA_MOOD_ANG_03_t9)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ANG_t10 = rowMeans(select(ws,
           c(DA_MOOD_ANG_01_t10,
             DA_MOOD_ANG_02_t10,
             DA_MOOD_ANG_03_t10)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(ANG = rowMeans(select(ws,
           c(ANG_t1,
             ANG_t2,
             ANG_t3,
             ANG_t4,
             ANG_t5,
             ANG_t6,
             ANG_t7,
             ANG_t8,
             ANG_t9,
             ANG_t10)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(SA_t1 = rowMeans(select(ws,
           c(DA_ANTC_01_t1,
             DA_ANTC_02_t1)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(SA_t2 = rowMeans(select(ws,
           c(DA_ANTC_01_t2,
             DA_ANTC_02_t2)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(SA_t3 = rowMeans(select(ws,
           c(DA_ANTC_01_t3,
             DA_ANTC_02_t3)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(SA_t4 = rowMeans(select(ws,
           c(DA_ANTC_01_t4,
             DA_ANTC_02_t4)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(SA_t5 = rowMeans(select(ws,
           c(DA_ANTC_01_t5,
             DA_ANTC_02_t5)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(SA_t6 = rowMeans(select(ws,
           c(DA_ANTC_01_t6,
             DA_ANTC_02_t6)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(SA_t7 = rowMeans(select(ws,
           c(DA_ANTC_01_t7,
             DA_ANTC_02_t7)),
           na.rm = TRUE))
```



```{r}
ws <- ws %>%
  mutate(SA_t8 = rowMeans(select(ws,
           c(DA_ANTC_01_t8,
             DA_ANTC_02_t8)),
           na.rm = TRUE))
```



```{r}
ws <- ws %>%
  mutate(SA_t9 = rowMeans(select(ws,
           c(DA_ANTC_01_t9,
             DA_ANTC_02_t9)),
           na.rm = TRUE))
```


```{r}
ws <- ws %>%
  mutate(SA_t10 = rowMeans(select(ws,
           c(DA_ANTC_01_t10,
             DA_ANTC_02_t10)),
           na.rm = TRUE))
```



```{r}
ws <- ws %>%
  mutate(SA = rowMeans(select(ws,
           c(SA_t1,
             SA_t2,
             SA_t3,
             SA_t4,
             SA_t5,
             SA_t6,
             SA_t7,
             SA_t8,
             SA_t9,
             SA_t10)),
           na.rm = TRUE))
```


```{r}
ws_use <- ws %>%
  select(ILWOTA, PSYSAFE, SA, ANG)

```


```{r}
summarytools::freq(ws$ST_GENDER)
```


```{r}
table(ws$ST_GENDER, useNA='ifany')
```


```{r}
ws %>% skim(ST_AGE)
```


```{r}
ws %>% 
  skim(
    ILWOTA, PSYSAFE, SA, ANG
  )
```


```{r}
cor_dat <- ws %>%
  select(ILWOTA, PSYSAFE, SA, ANG)

cor_dat

```

```{r}
cor_dat %>% corr.test()
```


```{r}
lm(SA~ILWOTA, data = ws) %>% 
  summary()
```

```{r}
ws <- ws %>%
  mutate(
    ILWOTA_s = scale(ILWOTA, center = T, scale = T)
    , SA_s = scale(SA, center = T, scale = T)
  )
```

```{r}
lm(
  SA_s ~ ILWOTA_s
  , data = ws
  ) %>% 
  summary()
```

```{r, eval=FALSE}
set.seed(42)
mediate(
  SA ~ ILWOTA + (ANG)
  , data = ws
) %>% print()
```

```{r}
ws <- ws %>%
  mutate(
    ILWOTA_c = scale(ILWOTA, center = T, scale = F)
    , PSYSAFE_c = scale(PSYSAFE, center = T, scale = F))
```

```{r}
lm(
  SA ~ ILWOTA_c * PSYSAFE_c
  ,  data = ws
  ) %>%
  summary()
```

```{r, eval=FALSE}
interact_plot(
  lm(
  SA ~ ILWOTA_c * PSYSAFE_c
  ,  data = ws
  )
  , pred = ILWOTA_c
  , modx = PSYSAFE_c
  , interval = T
)
```


```{r, eval=FALSE}
johnson_neyman(
  lm(
  SA ~ ILWOTA_c * PSYSAFE_c
  ,  data = ws
  )
  , pred = ILWOTA_c
  , modx = PSYSAFE_c
  ,control.fdr = T)
```


# Bootstrapping

Bootstrapping is an excellent way to get reliable/robust error estimations without distributional assumptions.

This workshop included three analyses: 

* simple linear regression
* mediation
* moderation

The *mediation* already utilizes bootstrapping (multiplying the two parameters results in an indirect path with non-normal distributed errors, so bootstrapping is required). 
For the two other analyses, I  will briefly demonstrate how to rewrite the code so that it uses bootstrapping.

## Preparation

First we install the `lmboot` package. There are many other ways/packages to do bootstrapping in  R, but this is one of easiest for `lm` objects.

```{r, echo=TRUE, results='asis'}
install_load("lmboot")
```

Next, we set a seed, so that our results stay the same from run to run.

```{r, echo=TRUE, results='asis'}
seed <- 42
```

## simple linear regression

The original looked like this:


```{r, echo=TRUE, results='asis'}
lm(
  SA_s ~ ILWOTA_s
  , data = ws
  ) %>% 
  summary()
```

The bootstrapped version looks like that:

```{r}
ws  %>% 
  select(SA_s, ILWOTA_s) %>%
  mutate_all(as.vector)

```


```{r, echo=TRUE, results='asis'}
boot_simple_reg <- residual.boot(
     SA_s ~ ILWOTA_s
    , data = ws  %>% 
      # this part is a little awkward - scale() does not return a vector but a one-dimensional matrix
      # this is mostly irrelevant, because the look and feel alike,
      # but lmboot cannot deal with it, therefore we need to transform the columns into vectors
      select(SA_s, ILWOTA_s) %>% 
      mutate_all(as.vector) %>%
      # and it cannot deal with missings
      # so either remove or impute them
      drop_na()
    , seed = seed
  )


#plot the sampling distribution of the slope coefficient
hist(boot_simple_reg$bootEstParam[,2], main="Residual Bootstrap Sampling Distn.",
xlab="Slope Estimate")

#bootstrap 95% CI for slope parameter (percentile method)
quantile(boot_simple_reg$bootEstParam[,2], probs=c(.025, .975))

```

Since **0** is not included the confidence 95%-interval [2.5% - 97.5%] the result is significant on a alpha level of 5%.  


## moderation

The original moderation  analysis looked like  that:

```{r, echo=TRUE, results='asis'}
lm(
  SA ~ ILWOTA_c * PSYSAFE_c
  ,  data = ws
  ) %>%
  summary()
```

The bootstrapped version looks like that:

We start by performing the analysis

```{r, echo=TRUE, results='asis'}
boot_moderation <- residual.boot(
     SA ~ ILWOTA_c * PSYSAFE_c
    , data = ws  %>% 
      # this part is a little awkward - scale() does not return a vector but a one-dimensional matrix
      # this is mostly irrelevant, because the look and feel alike,
      # but lmboot cannot deal with it, therefore we need to transform the columns into vectors
      select(SA, ILWOTA_c, PSYSAFE_c) %>% 
      mutate_all(as.vector) %>%
      # and it cannot deal with missings
      # so either remove or impute them
      drop_na()
    , seed = seed
  )
```

Since there are more parameters we check there sequence. 

```{r, echo=TRUE, results='asis'}
boot_moderation$bootEstParam  %>% colnames()
```

### Result for  `ILWOTA_c` 

```{r, echo=TRUE, results='asis'}
quantile(boot_moderation$bootEstParam[,2], probs=c(.025, .975))
```

->  0 not included -> significant

### Result for  `PSYSAFE_c`

```{r, echo=TRUE, results='asis'}
quantile(boot_moderation$bootEstParam[,3], probs=c(.025, .975))
```

->  0 included -> not significant

### Result for  `ILWOTA_c:PSYSAFE_c` (the interaction)

```{r, echo=TRUE, results='asis'}
quantile(boot_moderation$bootEstParam[,4], probs=c(.025, .975))
```

->  0 included -> not significant